Toxic Code Snippets on Stack Overflow

### 2018-05-24 cloverflow-tse/cloverflow.tex
Another round of revision on the TSE paper.

	\item \textbf{An investigation of toxic code snippets on Stack Overflow:} Our study shows that from
	the 2,289 online clones, at least 328 have been copied from open source
	projects or external online sources to Stack Overflow, potentially violating
	software licenses. For 153 of them, we found evidence that they have been copied
	from a specific open source project. 100 of them we found to be outdated. %
	% and questionable for being reused.

@@

%\subsection{Experimental Setup}
%\vspace{1ex}
To answer these five research questions, we perform two surveys and an empirical study to
understand the developers' awareness of toxic code snippets on Stack Overflow and to
empirically study the online code clones between Stack Overflow and open source
projects and their toxicity.

@@

\textbf{The visitors' survey}
The survey consists of 16 questions: 9 Likert's
scale questions, 3 yes/no questions, 2 multiple-choice questions, and 2
open-ended questions. 
The first four questions are mandatory while the other 12
questions will be shown to the participants based on their previous answers. 
The survey collects information about the participant's software development
experience, the importance of Stack Overflow, reasons for reusing Stack Overflow
snippets, problems from Stack Overflow snippets, licensing of code on Stack
Overflow, and additional feedback. 
The full survey can be found in our research note~\cite{Ragkhitwetsagul_RN2017}.
We adopted non-probability convenient sampling to invite participants for this
survey. Participation in the survey requires experience of visiting Stack
Overflow for solving programming tasks at least once. The participants were
invited to take the survey via five channels: social media post (Facebook),
\textsf{blognone.com} (a popular technology news and media community in Thailand), 
the University of Molise in Italy where the third author
works, the \texttt{comp.lang.java.programmer} group and the Software Engineering
Facebook page. 
The survey was open for participation for 2 months 
from 25 July 2017 to 25 September 2017.

@@

\textbf{Stack Overflow:} We extracted Java code snippets from a snapshot of a
Stack Overflow dump\footnote{\url{https://archive.org/details/stackexchange}} in
January 2016. % The archived dump has a size of 9 gigabytes.
The data dump is in XML, and it contains information of posts (questions and
answers). We were interested in code snippets embedded in posts which were
located between {\small\texttt{<code>}...\texttt{</code>}} tags. A Stack
Overflow thread contains a question and several answers. An answer can also be
marked as an \textbf{accepted answer} by the questioner if the solution fixes
his/her problem. We collected Java code snippets using two criteria. First, we
only focused on code snippets in accepted answers. We chose the snippets in
accepted answers because they actually solved the problems in the questions.
Moreover, they are usually displayed just below the questions which makes them
more likely to be reused than other answers. Second, we were only interested in
code snippets of at least ten lines. Although the minimum clone size of six
lines is usual in clone detection~\cite{Bellon2007,Wang2013,Koschke2006}, we
empirically found that snippets of six lines contain a large number of
boiler-plate code of getters/setters, \texttt{equal} or \texttt{hashCode}
methods, which are not interesting for the study. Each snippet was extracted
from the dump and saved to a file. Moreover, we filtered out irrelevant code
snippets that were part of the accepted answers but were not written in Java by
using regular expressions and manual checking.
Finally, we obtained 72,365 Java code snippets containing 1,840,581
lines\footnote{Measured by cloc: \url{https://github.com/AlDanial/cloc}} of Java
source code. The median size of the snippets is 17 lines.

@@

Nevertheless, we investigated a crucial parameter setting for clone detection: 
the minimum clone size threshold.
Choosing a large threshold value can reduce the number of trivial clones
(e.g.,~\texttt{equals}, \texttt{hashCode}, or getter and setter methods) and
false clones in the analysis or the manual investigation
phase~\cite{Sajnani2016}, while at the same time may create some false negatives,
i.e.,~increasing precision. On the other hand, setting a low threshold
results in a larger number of clone candidate pairs to look at, i.e.,~increasing recall, 
and a higher chance of getting false positives. 
%It is known that lowering the threshold value 
%is harmful to precision. 
Moreover, the large number of clone
pairs will hinder the full manual validation of the clones.
% and one needs to
%rely on sampling of clone pairs. 
Three threshold values, six, ten, and fifteen lines, were chosen for our
investigation. We started our investigation by using a threshold value of six
lines, a well-accepted minimum clone size in clone benchmark~\cite{Bellon2007}.
Simian reported 67,172 clone candidate pairs and SourcererCC reported 7,752
clone candidate pairs. We randomly sampled 382 pairs from the two sets for
a manual check. This sample number was a statistically significant sample with a
95\% confidence level and $\pm 5\%$ confidence interval. The first author
investigated the sampled clone pairs and classified them into three groups:
non-clones, trivial clones (\texttt{equals}, \texttt{hashCode}, or getter and
setter methods), and non-trivial clones. The manual check found 26 non-clone
pairs; 322 trivial clone pairs and 34 non-trivial clone pairs. Next, we increased the
threshold to ten lines, another well-established minimum clone size for
large-scale data sets~\cite{Sajnani2016}, and retrieved 721 clone pairs from
Simian and 1,678 clone pairs from SourcererCC. We randomly sampled and manually
checked the same amount of 382 pairs and found 27 non-clone pairs, 253 trivial
clone pairs, and 102 non-trivial clone pairs. Then, we increased the threshold
further to fifteen lines and retrieved 196 clone pairs from Simian and 1,230
clone pairs from SourcererCC. The manual check of the 382 randomly sampled pairs
revealed zero non-clone pairs, 298 trivial clone pairs, and 83 non-trivial clone
pairs.

@@

The threshold \textit{t} is crucial for the ok-match because it affects the number
of merged clone pairs. Setting a high \textit{t} value will result in a few ok-match clone pairs
and duplicates of the same clone pairs (which are supposed to be merged) may appear in the merged
clone set. On the other hand, setting a low \textit{t} value will result in many ok-match clone
pairs, and some non-duplicate clone pairs may be accidentally merged by only
a few matching lines.
In order to get an optimal $t$ value, we did an analysis by choosing
five $t$ values of 0.1, 0.3, 0.5, 0.7, and 0.9 and studied the clone candidates.
By setting $t=0.7$ according to Bellon's study, we
found 97 ok-match pairs reported. On the other hand, setting $t$ to 0.1, 0.3,
0.5, and 0.9 resulted in 111, 110, 110, and 94 ok-matched pairs respectively.
Since the clone pairs of $t=0.1$ were the superset of other sets,  we manually
checked all the 111 reported pairs. We found one false positive pair and 110
true positive pairs. By raising the $t$ to 0.3 and 0.5, we got rid of the false
positive pair and still retained all the 110 true positive pairs. All the clone
pairs of $t=0.7$ (97) and $t=0.9$ (94) were also true positives due to being a
subset of $t=0.5$. However, since there were fewer merged clone pairs, 
we ended up leaving some duplicates of the same clones in the final merged clone set.
With this analysis, we can see that setting the threshold $t$ to 0.1 is too
relaxed and results in having false positive ok-match pairs, while setting the
$t$ to 0.7 or 0.9 is too strict. Thus,
we decided to select the $t$ value at 0.5.

@@

We found that although the answerers have been notified of outdated code in their
answers, for 51.5\% of them such notifications occur very rarely (only 1--20\%
of the answers). Only 3 participants reported that they were notified in more
than 60\% of their answers. This notification to the answerer can be done 
via several means, such as contacting the author directly, 
writing a comment saying that the answer is
already outdated, down-voting the answer or posting a newer answer.
The low percentage of outdated code notifications
reflect the experience of high reputation answerers who accumulate the reputation for a
long time. Due to the voting mechanism of Stack Overflow, high reputation users
usually provide high-quality answers to earn upvotes from other users. They are
careful when posting code snippets in the answer to avoid problems and, vice versa, 
getting downvotes. It would be interesting to compare the findings to
Stack Overflow answerers who are newer and have a lower reputation. However, we
leave it to future work.

@@

We received answers from 89 participants. 
Two participants never
copy code from Stack Overflow, so we analysed the answers of the remaining 87
participants.

@@

We analysed the time it took for the clone to appear from Qualitas
projects to Stack Overflow. The clone ages were calculated by counting the
number of months between the date of each Qualitas project and the date the answer
was posted on Stack Overflow as shown in~\ref{fig:boxplotcloneage}.
We found that, on average, it took the clones around 2 years since they appeared
in Qualitas projects to appear on Stack Overflow answers. Some of the clones
appeared on Stack Overflow almost at the same time as the original, while the
oldest clones took around 5 years.

@@

\textbf{EX: External Sources.} We found 197 clone pairs from external sources to
Stack Overflow. After consolidating duplicated SO snippets due to multiple
intra-clone instances in Qualitas, we obtained 109 EX pairs. We found
evidence of copying from an external source to both Stack
Overflow and Qualitas in 49 pairs. Each of the pairs contains
statement(s) pointing to the original external location of the cloned
code in Qualitas and Stack Overflow. Besides, we found evidence
of copying from an external source to Stack Overflow, but not in
Qualitas, in 60 pairs. 
Our
analysis shows that the external sources fall into six groups as displayed in
\Cref{fig:ex_sources}. There are 63 EX online clone pairs copied
from source code of Java SDK (e.g.,\ \textsf{java.util}, \textsf{javax.swing}, \textsf{javax.servlet}), 
18 pairs from websites, 14 pairs from open
source systems not in Qualitas (e.g.,\ \textsf{Mozilla
	Rhino}), 10 pairs from Java official documentation from Sun
Microsystems or Oracle, 3 pairs from books, and 1 pair from a company
project. For example, Stack Overflow Post 9549009 contains a code comment saying
\textit{``Copied shamelessly from
	org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator''} which is an
open source project not included in the Qualitas corpus. Post 92962 includes a {\small\texttt{VerticalLabelUI}}
class with a license statement showing that it is developed by a private company
called \textsf{Sapient}. Post 12879764 has a text saying \textit{``Code modified
	and cleaned from the original at Filthy Rich Clients.''} which is a book for
developing animated and graphical effects for desktop Java applications. Another
example is a copy of the code from a website in post 15260207. The text surrounding
source code reads ``\textit{I basically stole this from the web and modified it
	slightly... You can see the original post here
	(\url{http://www.java2s.com/Code/Java/Swing-JFC/DragListDemo.htm}).}''.
Interestingly, the code is actually a copy from Sun Microsystems.

@@

Moreover, using the information in git commit messages, we can associate each
change to its respective issues in an issue tracking system, such as Bugzilla or
Jira. We found that in 58 cases, the cloned code snippets on Stack Overflow were
changed because of a request in the issue tracking system. Since issue tracking
systems are also used, besides bug reports, for feature request and feature
enhancements, having an issue tracking ID can reflect that most of the changes are important
and not only a superficial fix such as code formatting. The intent behind
the changes are grouped into six categories as shown in \Cref{tab:intent_outdated}.
Enhancement is the majority intent accounting for 65 of the 100 outdated code (65\%), followed 
by code deprecation (15\%). There were 10 outdated code snippets (10\%) caused by bug fixing.
The rest of the changes are because of code refactoring (6\%), changing coding style (3\%), and 
data format change (2\%).
Not all outdated code is toxic. However, the 10 buggy and outdated code snippets 
we found are toxic and are harmful to reuse.

@@

We performed a detailed investigation of the 100 outdated answers on Stack
Overflow two years after the snapshot we have (6 May 2018) 
on three aspects: newer or higher-voted answers and comments. We found
that there were 34 posts which contained newer answers and 5 posts which contained answers with a higher number of
votes than the outdated answers. However, 99 of the 100 outdated answers were still
marked as accepted answers. For the comments, we check if there is any comment
to mitigate or point out the toxicity of the outdated code snippets. We found
that, out of 100 answers, 6 answers had a comment saying the
code in the answer is outdated or containing issues, such as \textit{``spring
	3.1 stuff''}, \textit{``...tried this but having connect exception --
	\texttt{javax.mail.MessagingException}:\textit{ Could not connect to SMTP host:
	\texttt{smtp.gmail.com}, port: 465''}, ``You should add a \texttt{buffer.reset(null, 0, 0);} at the end of the try block to avoid excess heap usage (issue no. HADOOP-11323)''} or \textit{``.. I do not have experience
	with new versions of hibernate for a long time. But previously without clean you
	could receive some unexpected results. So I suggest to try different approaches
	or even check latest documentation''}. The 6 outdated code snippets were still
not fixed, but the comments themselves may help to warn other Stack Overflow
users.

@@

Then, we performed code clone detection between the 100 outdated code snippets and 130,703 GitHub projects.
We found 102 cloned candidates, which were associated with 30 outdated code snippets, 
appearing in 68 GitHub projects and manually investigated all
of them. As shown in \Cref{tab:outdated_github}, out of the 102 cloned snippets,
13 cloned snippets matched with themselves because some of the Qualitas
projects also appear on GitHub. For other projects besides the Qualitas
projects, 32 cloned snippets were not exactly the same
(e.g.,~they contained additional code modifications made by the projects'
developers, or they were copied from another source with a slightly different code).
47 cloned snippets were the same as the
outdated code snippets, which of 12 were buggy.
Two cloned snippets gave attributions to Stack Overflow. The attributions
pointed to different posts than the ones we found but containing the same code
in the answers\footnote{The answers were not marked as accepted so they were not 
included in our experiment.}. 32 cloned snippets were very likely to be a file-level
clone from its respective original project (e.g.,~JFreeChart, JUnit, Log4J,
Hadoop) based on their license header and the Javadoc comments. 
13 cloned snippets did not have any hints or evidence of copying.

@@

\begin{boxquote}
For RQ4, our results show that 66\% (101) of QS clone pairs on Stack
Overflow are outdated. 86 pairs differ from their newest versions by
modifications applied to variable names or method names, added or deleted
statements, to a fully rewritten code with new method signatures. 15~pairs are
dead snippets. 47 outdated code snippets are found in 130,703 GitHub projects
without evidence of copying. Twelve were buggy. Two of them contains a race condition and
are found in popular projects: deeplearning4j and Apache Hive.
\end{boxquote}

@@

The same GitHub study has been done for license-incompatible code snippets. 
We detected clones between the 214
code snippets with their original license missing (86 QS, 78 EX, and 50 UD)  and
130,703 GitHub projects using SourcererCC with 80\% similarity threshold.
Opposite to the outdated clones, we discovered a large number
of 7,207 clone pairs. There were 95 pairs from 10 Qualitas projects hosted on
GitHub and 7,112 pairs from 2,427 other projects. Shown in
\Cref{tab:license_github}, the clones were found in highly-starred
projects (29,465 to 10 stars) to 1-star projects.
We found 12 code snippets with attributions to Stack Overflow questions/answers and
6 of them refer to one of our QS or EX clone pairs.
We used the Ninka tool to identify software licenses of the 7,207 cloned
code snippets automatically. 
Five code snippets did not have a license while the originals had the Apache-2, GPLv2,
or EPLv1 license. One snippet had the AGPLv3 license while the original had the Apache-2 license.
Only 995 code snippets in GitHub projects have the same license
as the originals in Qualitas.

\begin{table}
	\centering
	\label{tab:license_github}
	\begin{tabular}{lrrrrr}
		\toprule
		\multirow{2}{*}{No. of stars} & \multicolumn{2}{c}{Qualitas} & \multicolumn{3}{c}{Other Projects} \\ \cmidrule{2-6}
		& Projects & Pairs & Projects & Pairs & Same license \\
		\midrule
		29,540--10 & 8 & 71 & 406 & 1,837 & 193 \\
		9--5 & 0 & 0 & 275 & 739 & 110 \\
		4--1 & 2 & 24 & 1,746 & 4,536 & 692 \\
		\midrule
		Total & 10 & 95 & 2,427 & 7,112 & 995 \\
		\bottomrule
	\end{tabular}
	\caption{Clones of the 214 Stack Overflow missing-license code snippets in 131,703 GitHub projects}
\end{table}

@@

\subsubsection{Toxicity of outdated and license-incompatible clones}
We found only a small number of toxic outdated code snippets in open source projects on
GitHub. Besides 12 buggy and outdated code snippets found in 12 projects, the
rest were non-harmful clones of the outdated code. Although other studies show
that Stack Overflow code snippets may become toxic by containing security
vulnerabilities~\cite{Acar2016,Fischer2017} or API misuse~\cite{Zhang2018}, we
found in this study that the damage caused by outdated code on Stack
Overflow is not high.

On the other hand, the missing licensing statements of online code clones on
Stack Overflow can cause more damage than outdated code. As shown in our study and
also in the study by An et al. \cite{An2017}, some online clones on Stack Overflow are
initially licensed under more restrictive license than Stack Overflow's CC
BY-SA 3.0. If these missing-license online clones are reused in software with
an incompatible license, the software owner may face legal issues. Software
auditing services such as Black Duck Software or nexB, which can effectively
check for license compliance of code copied from open source projects, do not
check for the original license of the cloned code snippets on Stack Overflow. Although
the Stack Overflow answerers who participated in our survey believe that most of the
code snippets on Stack Overflow are too small to claim for copyright and they
fall under fair-use, there is still a risk due to different legal systems in each
country. For example, Germany's legal system does not have a concept of fair use.
Besides, the number of minimum lines of code to be considered copying, i.e.,~de minimis,
is also differently interpreted from case to case or from country to country.

@@

Online code clones are clones that have been copied to Q\&A websites
such as Stack Overflow. 
% They are similar to classical clones in software
% projects where they can be outdated and violating software license but
% are much harder to detect. 
We classified 2,289 clone pairs using seven patterns of online code
cloning. We discovered 154 clone pairs that have been
copied, with evidence, from Qualitas projects to Stack Overflow, 111
clone pairs that have been copied from external sources besides
Qualitas to Stack Overflow, and 65 clone pairs that are highly
similar but without evidence of copying.

We performed a detailed analysis of the online clone pairs on two
aspects: outdated code and potential license violation. The investigation of
the 154 clone pairs copied, with evidence, from Qualitas to Stack
Overflow reveals that 101 of them are outdated.  Moreover, we found 214
code snippets on Stack Overflow that could potentially violate the license of their
original software.

>>>>

	\item \textbf{An investigation of toxic code snippets on Stack Overflow:} Our study shows that from
	the 2,289 online clones, at least 328 have been copied from open source
	projects or external online sources to Stack Overflow, potentially violating
	software licenses. For 153 of them, we found evidence that they have been copied
	from a specific open source project. 100 of them were found to be outdated. %
	% and questionable for being reused.

@@

%\subsection{Experimental Setup}
%\vspace{1ex}
To answer these five research questions, we perform two surveys and an empirical study to
understand the developers' awareness of toxic code snippets on Stack Overflow and to
empirically study the online code clones between Stack Overflow and open source
projects, and their toxicity.

@@

\textbf{The visitors' survey}
The survey consists of 16 questions: 9 Likert's
scale questions, 3 yes/no questions, 2 multiple-choice questions, and 2
open-ended questions. 
The first four questions are mandatory while the other 12
questions will be shown to the participants based on their previous answers. 
The survey collects information about the participant's software development
experience, the importance of Stack Overflow, reasons for reusing Stack Overflow
snippets, problems from Stack Overflow snippets, licensing of code on Stack
Overflow, and additional feedback. 
The full survey can be found in our research note~\cite{Ragkhitwetsagul_RN2017}.
We adopted non-probability convenient sampling to invite participants for this
survey. Participation in the survey requires experience of visiting Stack
Overflow for solving programming tasks at least once. The participants were
invited to take the survey via five channels: social media post (Facebook),
\textsf{blognone.com} (a popular technology news and media community in Thailand), 
the University of Molise in Italy where the third author
works, the \texttt{comp.lang.java.programmer} group, and the Software Engineering
Facebook page. 
The survey was open for participation for 2 months 
from 25 July 2017 to 25 September 2017.

@@

\textbf{Stack Overflow:} We extracted Java code snippets from a snapshot of a
Stack Overflow dump\footnote{\url{https://archive.org/details/stackexchange}} in
January 2016. % The archived dump has a size of 9 gigabytes.
The data dump is in XML, and it contains information about posts (questions and
answers). We were interested in code snippets embedded in posts which were
located between {\small\texttt{<code>}...\texttt{</code>}} tags. A Stack
Overflow thread contains a question and several answers. An answer can also be
marked as an \textbf{accepted answer} by the questioner if the solution fixes
his/her problem. We collected Java code snippets using two criteria. First, we
only focused on code snippets in accepted answers. We chose the snippets in
accepted answers because they actually solved the problems in the questions.
Moreover, they are usually displayed just below the questions which makes them
more likely to be reused than other answers. Second, we were only interested in
code snippets of at least ten lines. Although the minimum clone size of six
lines is usual in clone detection~\cite{Bellon2007,Wang2013,Koschke2006}, we
empirically found that snippets of six lines contain a large number of
boiler-plate code of getters/setters, \texttt{equal} or \texttt{hashCode}
methods, which are not interesting for the study. Each snippet was extracted
from the dump and saved to a file. Moreover, we filtered out irrelevant code
snippets that were part of the accepted answers but were not written in Java by
using regular expressions and manual checking.
Finally, we obtained 72,365 Java code snippets containing 1,840,581
lines\footnote{Measured by cloc: \url{https://github.com/AlDanial/cloc}} of Java
source code. The median size of the snippets is 17 lines.

@@

Nevertheless, we investigated a crucial parameter setting for clone detection: 
the minimum clone size threshold.
Choosing a large threshold value can reduce the number of trivial clones
(e.g.,~\texttt{equals}, \texttt{hashCode}, or getter and setter methods) and
false clones in the analysis or the manual investigation
phase~\cite{Sajnani2016}, i.e.,~increasing precision. 
Nonetheless, it may create some false negatives. 
On the other hand, setting a low threshold
results in a larger number of clone candidate pairs to look at, i.e.,~increasing recall, 
and a higher chance of getting false positives. 
%It is known that lowering the threshold value 
%is harmful to precision. 
Moreover, the large number of clone
pairs hinders a full manual validation of the clones.
% and one needs to
%rely on sampling of clone pairs. 
Three threshold values, six, ten, and fifteen lines, were chosen for our
investigation. We started our investigation by using a threshold value of six
lines, a well-accepted minimum clone size in clone benchmark~\cite{Bellon2007}.
Simian reported 67,172 clone candidate pairs and SourcererCC reported 7,752
clone candidate pairs. We randomly sampled 382 pairs from the two sets for
a manual check. This sample number was a statistically significant sample with a
95\% confidence level and $\pm 5\%$ confidence interval. The first author
investigated the sampled clone pairs and classified them into three groups:
non-clones, trivial clones (\texttt{equals}, \texttt{hashCode}, or getter and
setter methods), and non-trivial clones. The manual check found 26 non-clone
pairs, 322 trivial clone pairs, and 34 non-trivial clone pairs. Next, we increased the
threshold to ten lines, another well-established minimum clone size for
large-scale data sets~\cite{Sajnani2016}, and retrieved 721 clone pairs from
Simian and 1,678 clone pairs from SourcererCC. We randomly sampled and manually
checked the same amount of 382 pairs and found 27 non-clone pairs, 253 trivial
clone pairs, and 102 non-trivial clone pairs. Then, we increased the threshold
further to fifteen lines and retrieved 196 clone pairs from Simian and 1,230
clone pairs from SourcererCC. The manual check of the 382 randomly sampled pairs
revealed zero non-clone pairs, 298 trivial clone pairs, and 83 non-trivial clone
pairs.

@@

The threshold \textit{t} is crucial for the ok-match because it affects the number
of merged clone pairs. Setting a high \textit{t} value will result in a few ok-match clone pairs
and duplicates of the same clone pairs (which are supposed to be merged) may appear in the merged
clone set. On the other hand, setting a low \textit{t} value will result in many ok-match clone
pairs, and some non-duplicate clone pairs may be accidentally merged by only
a few matching lines.
In order to get an optimal $t$ value, we did an analysis by choosing
five $t$ values of 0.1, 0.3, 0.5, 0.7, 0.9 and studied the merged clone candidates.
By setting $t=0.7$ according to Bellon's study, we
found 97 ok-match pairs reported. On the other hand, setting $t$ to 0.1, 0.3,
0.5, and 0.9 resulted in 111, 110, 110, and 94 ok-matched pairs respectively.
Since the clone pairs of $t=0.1$ were the superset of other sets,  we manually
checked all the 111 reported pairs. We found one false positive pair and 110
true positive pairs. By raising the $t$ to 0.3 and 0.5, we got rid of the false
positive pair and still retained all the 110 true positive pairs. All the clone
pairs of $t=0.7$ (97) and $t=0.9$ (94) were also true positives due to being a
subset of $t=0.5$. However, since there were fewer merged clone pairs, 
we ended up leaving some duplicates of the same clones in the final merged clone set.
With this analysis, we can see that setting the threshold $t$ to 0.1 is too
relaxed and results in having false positive ok-match pairs, while setting the
$t$ to 0.7 or 0.9 is too strict. Thus,
we decided to select the $t$ value at 0.5.

@@

We found that although the answerers have been notified of outdated code in their
answers, for 51.5\% of them such notifications occur very rarely (only 1--20\%
of the answers). Only 3 participants reported that they were notified in more
than 60\% of their answers. This notification to the answerer can be done 
via several means, such as contacting the author directly or 
writing a comment saying that the answer is
already outdated.
The low percentage of outdated code notifications
reflect the experience of high reputation answerers who accumulate the reputation for a
long time. Due to the voting mechanism of Stack Overflow, high-reputation users
usually provide high-quality answers to earn upvotes from other users. They are
careful when posting code snippets in the answer to avoid problems and, vice versa, 
getting downvotes. It would be interesting to compare the findings to
Stack Overflow answerers who are newer and have a lower reputation. However, we
leave it to future work.

@@

We received answers from 89 participants. Two participants never copy code from
Stack Overflow, so we analysed the answers of the remaining 87 participants. We
only present a summary of the survey answers in this paper, and the full
analysis is available as a research note~\cite{Ragkhitwetsagul_RN2017}.

@@

We analysed the time it took for the clone to appear from Qualitas
projects to Stack Overflow. The clone ages were calculated by counting the
number of months between the date of each Qualitas project and the date the answer
was posted on Stack Overflow as shown in~\Cref{fig:boxplotcloneage}.
We found that, on average, it took the clones around 2 years since they appeared
in Qualitas projects to appear on Stack Overflow answers. Some of the clones
appeared on Stack Overflow almost at the same time as the original, while the
oldest clones took around 5 years.

@@

\textbf{EX: External Sources.} We found 197 clone pairs from external sources to
Stack Overflow. After consolidating duplicated SO snippets due to multiple
intra-clone instances in Qualitas, we obtained 109 EX pairs. We found
evidence of copying from an external source to both Stack
Overflow and Qualitas in 49 pairs. Each of the pairs contains
statement(s) pointing to the original external location of the cloned
code in Qualitas and Stack Overflow. Besides, we found evidence
of copying from an external source to Stack Overflow, but not in
Qualitas, in 60 pairs. 
Our
analysis shows that the external sources fall into six groups as displayed in
\Cref{fig:ex_sources}. There are 63 EX online clone pairs copied
from source code of Java SDK (e.g.,\ \textsf{java.util}, \textsf{javax.swing}, \textsf{javax.servlet}), 
18 pairs from websites, 14 pairs from open
source systems not in Qualitas (e.g.,\ \textsf{Mozilla
	Rhino}), 10 pairs from Java official documentation by Sun
Microsystems or Oracle, 3 pairs from books, and 1 pair from a company
project. For example, Stack Overflow Post 9549009 contains a code comment saying
\textit{``Copied shamelessly from
	org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator''} which is an
open source project not included in the Qualitas corpus. Post 92962 includes a {\small\texttt{VerticalLabelUI}}
class with a license statement showing that it is developed by a private company
called \textsf{Sapient}. Post 12879764 has a text saying \textit{``Code modified
	and cleaned from the original at Filthy Rich Clients.''} which is a book for
developing animated and graphical effects for desktop Java applications. Another
example is a copy of the code from a website in post 15260207. The text surrounding
source code reads ``\textit{I basically stole this from the web and modified it
	slightly... You can see the original post here
	(\url{http://www.java2s.com/Code/Java/Swing-JFC/DragListDemo.htm}).}''.
Interestingly, the code is actually a copy from Sun Microsystems.

@@

Moreover, using the information in git commit messages, we can associate each
change to its respective issues in an issue tracking system, such as Bugzilla or
Jira. We found that in 58 cases, the cloned code snippets on Stack Overflow were
changed because of a request in the issue tracking system. Since issue tracking
systems are also used, besides bug reports, for feature request and feature
enhancements, having an issue tracking ID can reflect that most of the changes are important
and not only a superficial fix such as code formatting. The intent behind
the changes are grouped into six categories as shown in \Cref{tab:intent_outdated}.
Enhancement is the majority intent accounting for 65 of the 100 outdated code (65\%), followed 
by code deprecation (15\%). There were 10 outdated code snippets (10\%) caused by bug fixing.
The rest of the changes are because of code refactoring (6\%), changing coding style (3\%), and 
the data format change (2\%).
Not all outdated code is toxic. However, the 10 buggy and outdated code snippets 
we found are toxic and are harmful to reuse.

@@

We performed a detailed investigation of the 100 outdated answers on Stack
Overflow, on 6 May 2018, approximately two years after the snapshot we analysed was created
to look for any changes, warnings, or mitigations made to the outdated code snippets.
We investigated the answers on three aspects: newer answers, higher-voted answers, and comments on the
outdated answers. We found
34 posts which contained newer answers and 5 posts which contained answers with a higher number of
votes than the outdated answers. However, 99 of the 100 outdated answers were still
marked as accepted answers. For the comments, we check if there is any comment
to mitigate or point out the toxicity of the outdated code snippets. We found
that, out of 100 answers, 6 answers had a comment saying the
code in the answer is outdated or containing issues, such as \textit{``spring
	3.1 stuff''}, \textit{``...tried this but having connect exception --
	\texttt{javax.mail.MessagingException}:\textit{ Could not connect to SMTP host:
	\texttt{smtp.gmail.com}, port: 465''}, ``You should add a \texttt{buffer.reset(null, 0, 0);} at the end of the try block to avoid excess heap usage (issue no. HADOOP-11323)''} or \textit{``.. I do not have experience
	with new versions of hibernate for a long time. But previously without clean you
	could receive some unexpected results. So I suggest to try different approaches
	or even check latest documentation''}. The 6 outdated code snippets were still
not fixed, but the comments themselves may help to warn some of the Stack Overflow
users.

@@

Then, we performed code clone detection between the 100 outdated code snippets and 130,703 GitHub projects.
We found 102 cloned candidates, which were associated with 30 outdated code snippets, 
appearing in 68 GitHub projects and manually investigated all
of them. Out of the 102 cloned snippets,
13 cloned snippets matched with themselves because some of the Qualitas
projects also appear on GitHub. For other projects besides the Qualitas
projects, 32 cloned snippets were not exactly the same
(e.g.,~they contained additional code modifications made by the projects'
developers, or they were copied from another source with a slightly different code).
47 cloned snippets were the same as the
outdated code snippets, which of 12 were buggy.
Two cloned snippets gave attributions to Stack Overflow. The attributions
pointed to different posts than the ones we found but containing the same code
in the answers\footnote{The answers were not marked as accepted so they were not 
included in our experiment.}. 32 cloned snippets were very likely to be a file-level
clone from its respective original project (e.g.,~JFreeChart, JUnit, Log4J,
Hadoop) based on their license header and the Javadoc comments. 
13 cloned snippets did not have any hints or evidence of copying.

@@

\begin{boxquote}
For RQ4, our results show that 66\% (101) of QS clone pairs on Stack
Overflow are outdated. 86 pairs differ from their newest versions by
modifications applied to variable names or method names, added or deleted
statements, to a fully rewritten code with new method signatures. 15~pairs are
dead snippets. 47 outdated code snippets are found in 130,703 GitHub projects
without evidence of copying, which of 12 were buggy. A toxic 
code snippet with a race condition was found in two popular projects: deeplearning4j and Apache Hive.
\end{boxquote}

@@

The same GitHub study has been done for license-incompatible code snippets. 
We detected clones between the 214
code snippets with their original license missing (86 QS, 78 EX, and 50 UD)  and
130,703 GitHub projects using SourcererCC with 80\% similarity threshold.
Opposite to the outdated clones, we discovered a large number
of 7,207 clone pairs. There were 95 pairs from 10 Qualitas projects hosted on
GitHub and 7,112 pairs from 2,427 other projects. As shown in
\Cref{tab:license_github}, the clones were found in highly-starred
projects (29,465 to 10 stars) to 1-star projects.
We found 12 code snippets with attributions to Stack Overflow questions/answers and
6 of them refer to one of our QS or EX clone pairs.
We used the Ninka tool to identify software licenses of the 7,112 cloned
code snippets automatically. 
Five code snippets did not have a license while the originals had the Apache-2, GPLv2,
or EPLv1 license. One snippet had the AGPLv3 license while the original had the Apache-2 license.
Only 995 code snippets in GitHub projects have the same license
as the originals in Qualitas.

\begin{table}
	\centering
	\begin{tabular}{lrrrrr}
		\toprule
		\multirow{2}{*}{No. of stars} & \multicolumn{2}{c}{Qualitas} & \multicolumn{3}{c}{Other Projects} \\ \cmidrule{2-6}
		& Projects & Pairs & Projects & Pairs & Same license \\
		\midrule
		29,540--10 & 8 & 71 & 406 & 1,837 & 193 \\
		9--5 & 0 & 0 & 275 & 739 & 110 \\
		4--1 & 2 & 24 & 1,746 & 4,536 & 692 \\
		\midrule
		Total & 10 & 95 & 2,427 & 7,112 & 995 \\
		\bottomrule
	\end{tabular}
	\caption{Clones of the 214 Stack Overflow missing-license code snippets in 131,703 GitHub projects}
	\label{tab:license_github}
\end{table}

@@

\subsubsection{Toxicity of outdated and license-incompatible clones}
The insights from our study of toxic code snippets on Stack Overflow are as follows:

\textbf{Outdated clones are not harmful:} We found only a small number of toxic outdated code snippets in open source projects on
GitHub. Besides 12 buggy and outdated code snippets found in 12 projects, the
rest were non-harmful clones of the outdated code. Although other studies show
that Stack Overflow code snippets may become toxic by containing security
vulnerabilities~\cite{Acar2016,Fischer2017} or API misuse~\cite{Zhang2018}, we
found in this study that the damage caused by outdated code on Stack
Overflow is not high.

\textbf{License-incompatible clones can be harmful:} The missing licensing statements of online code clones on
Stack Overflow can cause more damage than outdated code. As shown in our study and
also in the study by An et al. \cite{An2017}, some online clones on Stack Overflow are
initially licensed under more restrictive license than Stack Overflow's CC
BY-SA 3.0. If these missing-license online clones are reused in software with
an incompatible license, the software owner may face legal issues. Software
auditing services such as Black Duck Software or nexB, which can effectively
check for license compliance of code copied from open source projects, do not
check for the original license of the cloned code snippets on Stack Overflow. Although
the Stack Overflow answerers who participated in our survey believe that most of the
code snippets on Stack Overflow are too small to claim for copyright and they
fall under fair-use, there is still a risk due to different legal systems in each
country. For example, Germany's legal system does not have a concept of fair use.
Besides, the number of minimum lines of code to be considered copying, i.e.,~de minimis,
is also differently interpreted from case to case or from country to country.

@@

Online code clones are clones that have been copied to Q\&A websites
such as Stack Overflow. 
% They are similar to classical clones in software
% projects where they can be outdated and violating software license but
% are much harder to detect. 
We classified 2,289 clone pairs using seven patterns of online code cloning. We
discovered 153 clone pairs that have been copied, with evidence, from Qualitas
projects to Stack Overflow, 109 clone pairs that have been copied from external
sources besides Qualitas to Stack Overflow, and 65 clone pairs that are highly
similar but without evidence of copying.
